V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2022-01-04 src/ms.tex
fig placement f*ck*ng up arxiv
static not figures
linenumbers?
only line numbers in the acknowledgements?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{static/transits.pdf}
\caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black. \href{htt\
ps://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/transits.py}{\githubicon}} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{acknowledgments}
We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter. We thank Chas Beichman, Sarah Blunt, Jacob Bean, and Darryl Seligman for helpful comments on our \tess\ proposal (DDT 036) and thoughtful conversations. We thank our anonymous referee for their thoughtful insights which improved the quality of this manuscript. ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045).

@@

\end{acknowledgments}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{static/transits.pdf}
\caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black. \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/transits.py}{\githubicon}} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\begin{acknowledgments}
\vspace{0.5mm}

We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter. We thank Chas Beichman, Sarah Blunt, Jacob Bean, and Darryl Seligman for helpful comments on our \tess\ proposal (DDT 036) and thoughtful conversations. We thank our anonymous referee for their thoughtful insights which improved the quality of this manuscript. ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045).

@@

%\end{acknowledgments}
